An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-11 EconGrowth-R-Functions.Rnw
Improved documentation.

######################################
# Loads data and trims rows where necessary.
# Also, replaces the name of the desired energy column with "iEToFit".
# Returns a data.frame with the loaded data.
##
loadAndPrepDataForCES <- function(countryAbbrev, energyType){
print(paste("Inside loadAndPrepDataForCES. countryAbbrev =", countryAbbrev))
print(paste("missing(energyType) =", missing(energyType)))
  dataTable <- loadData(countryAbbrev)
print("loaded data")
  # Trim data from China and South Africa that is missing labor information for 2011.
  dataTable <- subset(dataTable, !is.na(iLabor))
print("Trimmed data")
  if (!missing(energyType)){
print("Inside if not missing energy type")
    if (energyType == "U"){
      # Trim the dataset to include only those years for which U is available.
      dataTable <- subset(dataTable, !is.na(iU))
    }
    # We need to do the CES fit with the desired energyType.
    # To achieve the correct fit, we'll change the name of the desired column
    # to "iEToFit" and use "iEToFit" in the nls function.
    dataTable <- replaceColName(dataTable, energyType, "iEToFit")
  }
print("right before return.")
  return(dataTable)
}

########################
# Returns a cesEst model (without energy) for the country specified.
##
cesModelNoEnergy <- function(countryAbbrev){
print(paste("Inside cesModelNoEnergy. countryAbbrev =", countryAbbrev))
  # Load the data that we need.
  dataTable <- loadAndPrepDataForCES(countryAbbrev)
  control=nls.lm.control(maxiter=1000, maxfev=2000)
  modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesWithoutEnergy, tName=tName, control=control)
  return(modelCES)
}

@@

print(paste("Inside cesModel. energyType is missing. countryAbbrev =", countryAbbrev))

>>>>

######################################
# Loads data and trims rows where necessary.
# Also, replaces the name of the desired energy column with "iEToFit".
# If you omit the energyType parameter, "iEToFit" will not appear in the column names, because
# it is assumed that you want a CES fit without an energy term.
# Returns a data.frame with the loaded data.
##
loadAndPrepDataForCES <- function(countryAbbrev, energyType){
  dataTable <- loadData(countryAbbrev)
  # Trim data from China and South Africa that is missing labor information for 2011.
  dataTable <- subset(dataTable, !is.na(iLabor))
  if (!missing(energyType)){
    if (energyType == "U"){
      # Trim the dataset to include only those years for which U is available.
      dataTable <- subset(dataTable, !is.na(iU))
    }
    # We need to do the CES fit with the desired energyType.
    # To achieve the correct fit, we'll change the name of the desired column
    # to "iEToFit" and use "iEToFit" in the nls function.
    dataTable <- replaceColName(dataTable, energyType, "iEToFit")
  }
  return(dataTable)
}

########################
# Returns a cesEst model (without energy) for the country specified.
##
cesModelNoEnergy <- function(countryAbbrev){
  # Load the data that we need.
  dataTable <- loadAndPrepDataForCES(countryAbbrev)
  control=nls.lm.control(maxiter=1000, maxfev=2000)
  modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesWithoutEnergy, tName=tName, control=control)
  return(modelCES)
}

@@
